Slitasje og kjørespor

### 2023-01-30 DRAFT_slitasjeOgKjørespor.Rmd
doc: Fill in meta data

### Original units
The

### Temporal coverage

### Aditional comments about the dataset

## Ecosystem characteristic

### Norwegain standard

### UN standard

<!-- Text here. Note that there are two parallell systems for defining ecosystem properties - one Norwegian and one international (SEEA EA). See man/SEEA EA examples.pdf for help -->

@@

7TK and 7SE use a 4 step scale ![Four step condition
scale](images/ninAR4b.PNG)

@@

#### Scaled variable

>>>>

### Original units
The variables are recorded on a coarse four-sped ordinal scale (Fig. \@ref(fig:four-step)).

### Temporal coverage
The data goes back to 2018, but is because of data shortage, it is bulked into one time step. I then use the mean date for the raw data, and define the variable as belonging to the year 2020 (read more [here](#scaled-slitasje-variable)).

### Aditional comments about the dataset
For a run through of the data set, see [here](#naturtyper)

## Ecosystem characteristic
### Norwegain standard
Primærproduksjon

The indicator is tagged to the _Økologisk egenskap_ called Primærproduksjon (Primary productivity). This is tentative, and perhaps _abiotiske forhold_ is more suited. But the thought behind the chiose is that _sliatsje_ affect the potential for primary productivity.

### UN standard
The indicator is tagged as a Physical state characteristics indicator. This is quite clear. It's a tpe of abiotic characteritic that has to do with the physical structure rather than the chemical composition.

@@

7TK and 7SE use a 4 step scale

```{r four-step, fig.cap="Four step condition scale"}
knitr::include_graphics("images/ninAR4b.PNG")
```

@@

#### Scaled variable {#scaled-slitasje-variable}
